### 2019-05-29 Presentation/present.Rnw
code cleaned in new_meta_analysis.R

<<include = FALSE>>= 
library(knitr)
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

load(file.path(PATH_RESULTS, file = "data.processed.RData"))

require(tidyverse)
require(meta)
require(xtable)

meta.id <- function(meta.id.tolook){
	dt <- data.ext %>% filter(meta.id == meta.id.tolook)
	if(any(is.na(dt$events1)) | all(dt$events1 == 0)){
		meta.ex <- metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2, studlab = study.name, data = dt)
	} else{
		meta.ex <- metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2, studlab = study.name, sm = "RR", data = dt, method = "Inverse")
	}
	return(meta.ex)
}

funnel.id <- function(meta.id.tolook){
	funnel(meta.id(meta.id.tolook))
}

trimfill.id <- function(meta.id.tolook){
	funnel(trimfill(meta.id(meta.id.tolook)))
}

limitmeta.id <- function(meta.id.tolook){
	funnel(limitmeta(meta.id(meta.id.tolook)))
}

copas.id <- function(meta.id.tolook){
	auto.copas(meta.id(meta.id.tolook), 0.1)
}

setting.id <- function(meta.id.tolook){
	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(comparison.name, comparison.nr, outcome.name, sungroup.name))
}

est.id <- function(meta.id.tolook){
	return(meta %>% filter(meta.id == meta.id.tolook) %>% select(est.fixef, est.ranef, est.copas, est.trimfill.fixef, est.reg.ranef))
}

single.study.id <- function(meta.id.tolook){
	return(print(data.ext %>% filter(meta.id == meta.id.tolook) %>% select(study.name, effect, se, total1, total2, events1, events2, mean1, mean2) %>% 
							 	arrange(se), n = 200))
}

>>>>

<<include = FALSE>>= 
library(knitr)
rm(list = ls())
PATH_HOME = path.expand("~") # user home
PATH = file.path(PATH_HOME, 'Data/PubBias')
PATH2 = file.path(PATH_HOME, 'PubBias')
FILE = 'cochrane_2018-06-09.csv'
PATH_DATA = file.path(PATH, 'data')
PATH_CODE = file.path(PATH2, 'code')
PATH_RESULTS = file.path(PATH2, 'results')
PATH_FIGURES = file.path(PATH_RESULTS, 'figures')

@@

load(file.path(PATH_RESULTS, file = "mly.RData"))
load(file.path(PATH_RESULTS, file = "data.processed.RData"))

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
	load(file.path(PATH_RESULTS, file.bin))
} else {
	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
	load(file.path(PATH_RESULTS, file.cont))
} else {
	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

file.meta <- "meta.RData"
if (file.exists(file.path(PATH_RESULTS, file.meta))) {
	load(file.path(PATH_RESULTS, file.meta))
} else {
	meta <- pb.meta.merge(meta.bin, meta.cont)
	save(meta, file =  file.path(PATH_RESULTS, file.meta))
}

data.ext2 <- pb.process2(data)

### 2019-05-29 report/chapter03.Rnw
code cleaned in new_meta_analysis.R

# data = pb.readData(path = PATH_DATA, file = FILE)
# tmp = pb.clean(data)
# data = tmp[[1]]
# aliases = tmp[[2]]

@@

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
  load(file.path(PATH_RESULTS, file.bin))
} else {
  meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.05, sm = "OR")
  save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
  load(file.path(PATH_RESULTS, file.cont))
} else {
  meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.05)
  save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

@@

load(file.path(PATH_RESULTS, file = "data.processed.RData"))

require(biostatUZH)
require(tidyverse)
require(meta)
require(metasens)
require(gridExtra)
require(xtable)
@

>>>>

@@

load(file.path(PATH_RESULTS, file = "mly.RData"))
load(file.path(PATH_RESULTS, file = "data.processed.RData"))

file.bin <- "pb.bin.RData"
if (file.exists(file.path(PATH_RESULTS, file.bin))) {
	load(file.path(PATH_RESULTS, file.bin))
} else {
	meta.bin <- meta.bin.complete(data.ext, min.study.number = 10, sig.level = 0.1, sm = "RR")
	save(meta.bin, file =  file.path(PATH_RESULTS, file.bin))
}

file.cont <- "pb.cont.RData"
if (file.exists(file.path(PATH_RESULTS, file.cont))) {
	load(file.path(PATH_RESULTS, file.cont))
} else {
	meta.cont <- meta.cont.complete(data.ext, min.study.number = 10, sig.level = 0.1)
	save(meta.cont, file =  file.path(PATH_RESULTS, file.cont))
}

@@

data.ext2 <- pb.process2(data)

#Meta filtering: 
metac.bin <- meta.bin %>% filter(n.sig.type.bin > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
metac.cont <- meta.cont %>% filter(n.sig.type.cont > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
metac <- meta %>% filter(n.sig.type > 1) %>% filter((se.max^2)/(se.min^2) > 4) %>% filter(I2 < 0.5)
@
